NFC and burnout in teachers - A replication and extension study

### 2021-08-30 Manuscript/Manuscript.Rmd
removed an outlier
Tried knitting fix but didn't work
LaTeX Error: File `tabu.sty' not found.

csl               : apa.csl # this is a workaround for a current bug in the papaja/Rmd software, which fails to shorten multiple authors to "et al."
---

@@

```{r objective2, echo=FALSE, message=FALSE, warning=FALSE}

@@

# Plot a big correlational matrix to check for non-linear associations that might have caused the bad model fit
  ggpairs(score_data[,c(2,3,4,5,9,10,15,19,23,27)], lower = list(continuous = my_fn))

@@

```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r exploratory2, echo=FALSE, message=FALSE, warning=FALSE}

>>>>

csl               : apa.csl # this is a workaround for a current bug in the papaja/Rmd software, which fails to shorten multiple authors to "et al."

header-includes   : \usepackage{tabu}
---

@@

```{r objective2, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}

@@

  # Plot a big correlational matrix to check for non-linear associations that might have caused the bad model fit
  multicorrplot <- ggpairs(score_data[,c(2,3,4,5,9,10,15,19,23,27)], lower = list(continuous = my_fn))

  # Remove the outlier
  score_data <- score_data[score_data$id != 161, ]

@@

```{r exploratory1, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}

@@

```{r exploratory2, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
